Re-fit

### 2023-01-15 scripts/r/04_refit/refit_jvc.Rmd
🐛 - fix error from unzipped file plus fix path

@@

beast_path <- "/Users/casillas/academia/research/in_progress/many_speech_analyses/many_analyses/./data/analyses/jvc/trapezia_cantonensis//audio_chunks/"

>>>>

unzip(here("data", "analyses", "jvc", "trapezia_cantonensis", "audio_chunks.zip"), exdir = here("data", "analyses", "jvc", "trapezia_cantonensis"))

@@

beast_path <- "./data/analyses/jvc/trapezia_cantonensis/audio_chunks/"
